Robust Subspace and Higher Moments Distances for Botnet Detection

### 2019-04-23 docs/papers/2019JNCA_m-rpca/2019JNCA_m-rpca.tex
robpca

\textbf{MD has been used for distance based anomaly detection with robust estimates} in many areas, and is commonly combined to Fast Minimum Covariance Determinant (Fast-MCD) algorithm \cite{rousseeuw1999fast} for robust estimates.

@@

Skewness and the kurtosis tests are very sensitive outlier detectors. The properties of the kurtosis can be used to identify clusters or outliers \cite{pena2010eigenvectors}, while skewness has been used as adjust factor for outlier detection \cite{hubert2008outlier}.

@@

\cite{hubert2008outlier} (Outlier detection for skewed data)

@@

The Mahalanobis Distance is a measure of the distance between a vector $\boldsymbol{x}$ and a distribution $\boldsymbol{X}$, introduced by P. C. Mahalanobis in 1936 \cite{mahalanobis1936generalized}. It is a multi-dimensional generalization for measuring how many standard deviations away $\boldsymbol{x}$ is from the mean $\boldsymbol{\bar{x}}$ and covariance $\boldsymbol{\hat{S}}$ of $\boldsymbol{X}$.

@@

Classical estimates can be so strongly affected by contamination that diagnostic tools, such as the Mahalanobis Distances, become unable to detect the outliers. Therefore, we need reliable and robust estimators that can resist outliers contaminated data. Minimum Covariance Determinant (MCD) \cite{rousseeuw1984least} is a robust estimator commonly used for computing Mahalanobis Distance in order to detect anomalies.

@@

Affine equivariant means that when the data are translated or subjected to a linear transformation, the resulting location and scatter will transform accordingly \cite{rousseeuw1984least,rousseeuw1999fast}.

@@

Its main use has started since the construction of the computationally efficient Fast-MCD algorithm \cite{rousseeuw1999fast}.

@@

The proof is given by Rousseeuw and Driessen \cite{rousseeuw1999fast}.

@@

>>>>

\textbf{MD has been used for distance based anomaly detection with robust estimates} in many areas, and is commonly combined to Fast Minimum Covariance Determinant (Fast-MCD) algorithm \cite{rousseeuw1999fastmcd} for robust estimates.

@@

Skewness and the kurtosis tests are very sensitive outlier detectors. The properties of the kurtosis can be used to identify clusters or outliers \cite{pena2010eigenvectors}, while skewness has been used as adjust factor for outlier detection \cite{hubert2009robustskewed}.

@@

ROBPCA \cite{hubert2005robpca} intends to identify outliers using PCA to reduce the data dimensions and plot the orthogonal distances versus the score distances, to flag outliers using an outlier map. However, ROBPCA flags many points as outlying when the original data is skewed. To overcome that issue, \cite{hubert2009robustskewed} propose ROBPCA-AO, which relies on an adjusted outlyingness based on robust skewness for flagging outliers....

@@

The Mahalanobis Distance is a measure of the distance between a vector $\boldsymbol{x}$ and a distribution $\boldsymbol{X}$, introduced by P. C. Mahalanobis in 1936 \cite{mahalanobis1936md}. It is a multi-dimensional generalization for measuring how many standard deviations away $\boldsymbol{x}$ is from the mean $\boldsymbol{\bar{x}}$ and covariance $\boldsymbol{\hat{S}}$ of $\boldsymbol{X}$.

@@

Classical estimates can be so strongly affected by contamination that diagnostic tools, such as the Mahalanobis Distances, become unable to detect the outliers. Therefore, we need reliable and robust estimators that can resist outliers contaminated data. Minimum Covariance Determinant (MCD) \cite{rousseeuw1984mcd} is a robust estimator commonly used for computing Mahalanobis Distance in order to detect anomalies.

@@

Affine equivariant means that when the data are translated or subjected to a linear transformation, the resulting location and scatter will transform accordingly \cite{rousseeuw1984mcd,rousseeuw1999fastmcd}.

@@

Its main use has started since the construction of the computationally efficient Fast-MCD algorithm \cite{rousseeuw1999fastmcd}.

@@

The proof is given by Rousseeuw and Driessen \cite{rousseeuw1999fastmcd}.

@@

say that more studies about skewness and subspace learning can be done in order to explore it inside algorithms and non gaussian data
